An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing

### 2019-08-26 0_main.tex
anonymization
title: system => framework
naive method ==> uniform technique

\documentclass[5p,twocolumn,10pt,times]{elsarticle}
\usepackage{amsmath}
\usepackage{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
%\modulolinenumbers[5]
\addtolength{\textheight}{8mm}
\addtolength{\textwidth}{4mm}
\addtolength{\voffset}{-10mm}
\addtolength{\hoffset}{-3mm}

@@

@@

%\title{A robust framework for variable extrusion width concentric toolpath generation}
\title{A parametric system for generating contour parallel toolpaths with adaptive extrusion width}

%\author{Paper ID: xxx}

\author[um,tud]{Tim Kuipers}
\author[tud]{Eugeni L. Doubrovski}
\author[tud]{Jun Wu}
\author[cuhk]{Charlie Wang{\corref{cor1}}}
\ead{cwang@mae.cuhk.edu.hk}
\cortext[cor1]{Corresponding author}
\address[um]{Ultimaker, Utrecht, The Netherlands}
\address[tud]{Department of Design Engineering, Delft University of Technology, The Netherlands}
\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}

@@

A naive strategy for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a constant width.
In the center of the outline shapes this naive strategy can result in underfill regions and overfill regions as wide as the nozzle size.
Existing techniques address these over- and underfill issues by locally extruding a small amount of material less or more in those regions.
However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture accurately.
We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.

@@

Our framework is shown to be able to emulate several methods discussed in related literature and it enables a wide range of other beading strategies.
We show that we can define a strategy which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
We show that our open source implementation exhibits computation times in the same order of magnitude as the naive method.
\end{abstract}

@@

 \temp{%Table of contents just for reviewing purposes
 \tableofcontents
 }

>>>>

\documentclass[preprint,5p,twocolumn,times]{elsarticle}
\usepackage{amsmath}
\usepackage{hyperref} % added [draft] to avoid compilation issues that happen if a link is split and appears in two pages
%\modulolinenumbers[5]
\addtolength{\textheight}{8mm}
\addtolength{\textwidth}{4mm}
\addtolength{\voffset}{-10mm}
\addtolength{\hoffset}{-3mm}

@@

	\usepackage{censor} % \censor

@@

%\title{A robust framework for variable extrusion width concentric toolpath generation}
\title{An algorithmic framework for generating contour parallel toolpaths with adaptive extrusion width for additive manufacturing}

%\author{Paper ID: xxx}
\author{Anonymized}

\iffalse
\author[um,tud]{Tim Kuipers}
\author[tud]{Eugeni L. Doubrovski}
\author[tud]{Jun Wu}
\author[cuhk]{Charlie Wang{\corref{cor1}}}
\ead{cwang@mae.cuhk.edu.hk}
\cortext[cor1]{Corresponding author}
\address[um]{Ultimaker, Utrecht, The Netherlands}
\address[tud]{Department of Design Engineering, Delft University of Technology, The Netherlands}
\address[cuhk]{Department of Mechanical and Automation Engineering, The Chinese University of Hong Kong, Hong Kong SAR, China}
\fi

@@

A simple technique for densely filling the outlines of a layer determines the toolpaths by performing inward offsets from the outline shape of a uniform width.
In the center of the outline shapes this simple technique can result in underfill regions and overfill regions as wide as the nozzle size.
Existing techniques address these over- and underfill issues by locally extruding a small amount of material less or more in those regions.
However, such methods inevitably generate extrusion toolpaths with widths wildly differing from the nozzle size, which are difficult to manufacture accurately.
We propose a framework which allows to define beading strategies which distribute the overfill and underfill required in each region over nearby toolpaths, so that we considerably reduce the amount of extrusion toolpaths with extreme widths.

@@

Our framework is shown to be able to emulate several methods discussed in related literature and it enables a wide range of other beading strategies.
We show that we can define a strategy which reduces the amount of overfill and underfill compared to previous literature and we show that the extrusion widths have less deviation from the nozzle size.
We show that our open source implementation exhibits computation times in the same order of magnitude as the state-of-the-art implementation of the uniform width technique.
\end{abstract}

@@

 %\temp{%Table of contents just for reviewing purposes
 %\tableofcontents
 %}

### 2019-08-26 12_conclusions_future_work.tex
naive method ==> uniform technique

The proposed beading strategy greatly improves the process planning for parts with thin contours, which often occur for exmaple in architectural models, prototypes for casings or microstructures.
On the other hand it leaves most of the toolpaths the same as the naive method in case of wide/large contours, which means that existing literature which relates process parameters with mechanical properties of the end part are still applicable.

>>>>

The proposed beading strategy greatly improves the process planning for parts with thin contours, which often occur for exmaple in architectural models, prototypes for casings or microstructures.
On the other hand it leaves most of the toolpaths the same as the uniform width technique in case of wide/large contours, which means that existing literature which relates process parameters with mechanical properties of the end part are still applicable.

### 2019-08-26 1_intro.tex
naive method ==> uniform technique

The naive method for generating the shape filling toolpaths of a layer consists in performing inward offsets with the radius of the the nozzle from the outline shape.
However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfill} areas.
See \cref{intro_wedge}(top).
Overfills cause a buildup of pressure in the mechanical extrusion system, which can result in bulges or even a full print failure.
Underfills on the other hand, can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are large compared to the whole part.
In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
Some such toolpath generation techniques have already been developed.

\begin{figure}\centering
\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_accuracy.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_widths.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_InwardDistributed_widths.png}
\caption{
Toolpaths for a wedge shape using the naive offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
Overfill in orange, underfill in azure, narrow beads in blue and wide beads in red.
The wedge shape can be read like a graph plot: for each model diameter we can read out the resulting over- or underfill if a model has thin features with that particular diameter.
}
\label{intro_wedge}
\end{figure}

@@

%\subsection{Contributions}
A polygonal shape with a width of a fractional multiple of the nominal bead width will always result in the bead widths deviating from the nominal bead width by the fractional part in total,
because the total of the widths of the beads must add up to the fractional width of the part in order to avoid under- or overfill.
We therefore propose a framework which makes it possible to distribute the fractional discrepancy over several beads, so that the beads are generally closer to the nominal width.
Our contributions are as follows:
\begin{itemize}
\item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any function which maps a model diameter to a number of beads and their widths.
\item A specific beading strategy function for this framework for:
\begin{itemize}
\item Accurately filling a 2D outline with extrusion beads
\item Reducing the overfill and underfill areas compared to the naive method
\item Reducing the amount of beads with greatly deviating width compared to existing literature
\item Promoting smooth toolpaths which are close to the nominal width toward the outline of the shape.
\end{itemize}
\end{itemize}

>>>>

The simple technique for generating the shape filling toolpaths of a layer consists in performing uniform inward offsets with the radius of the the nozzle from the outline shape.
However, for geometrical features which are not an exact multiple of the nozzle size this method produces areas where an extrusion bead is placed twice: \emph{overfill} areas; and other areas which are not filled at all: \emph{underfill} areas.
See \cref{intro_wedge}(top).
Overfills cause a buildup of pressure in the mechanical extrusion system, which can result in bulges or even a full print failure.
Underfills on the other hand, can cause a drastic decrease in the part stiffness or even for small features not to be printed at all.
These problems are exacerbated for models with layer outlines with small features, because the over- and underfill areas are large compared to the whole part.
In order to avoid over- and underfills in regions which are not as wide as an exact multiple of the nozzle size we need algorithms which produce toolpaths which employ adaptive bead width.
Some such toolpath generation techniques have already been developed.

\begin{figure}\centering
\includegraphics[width=\columnwidth]{sources/intro/TEST_naive_accuracy.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_Center_widths.png}
\includegraphics[width=\columnwidth]{sources/intro/TEST_InwardDistributed_widths.png}
\caption{
Toolpaths for a wedge shape using the uniform offsetting approach (top), the approach by \citeauthor{Jin2017JMS}(middle) and our approach (bottom).
Overfill in orange, underfill in azure, narrow beads in blue and wide beads in red.
The wedge shape can be read like a graph plot: for each model diameter we can read out the resulting over- or underfill if a model has thin features with that particular diameter.
}
\label{intro_wedge}
\end{figure}

@@

%\subsection{Contributions}
A polygonal shape with a width of a fractional multiple of the nominal bead width will always result in the bead widths deviating from the nominal bead width by the fractional part in total,
because the total of the widths of the beads must add up to the fractional width of the part in order to avoid under- or overfill.
We therefore propose a framework which makes it possible to distribute the fractional discrepancy over several beads, so that the beads are generally closer to the nominal width.
Our contributions are as follows:
\begin{itemize}
\item A geometric framework for generating densely filling contour-parallel toolpaths employing adaptive width, according to any function which maps a model diameter to a number of beads and their widths.
\item A specific beading strategy function for this framework for:
\begin{itemize}
\item Accurately filling a 2D outline with extrusion beads
\item Reducing the overfill and underfill areas compared to the uniform width technique
\item Reducing the amount of beads with greatly deviating width compared to existing literature
\item Promoting smooth toolpaths which are close to the nominal width toward the outline of the shape.
\end{itemize}
\end{itemize}

### 2019-08-26 4_method.tex
lil fix of ref to non-existent fig
naive method ==> uniform technique

\section{Method}
\subsection{Overview}
The naive method consists of consecutive inward offsets from the outline using a constant bead width.
These offsets can be generated from the medial axis transform (MAT).
The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape. \cite{blum1967transformation}
The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
We can therefore use the MAT to efficiently calculate the consecutive offsets defining the naive toolpathing. \cite{eiamsa2003toward}

For the naive method the overfill and underfill problems arise in the center,
because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
Our framework can be seen as a way to change the mesh of the UoC such that the heights at the center are aligned with the slicing planes.

@@

Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous,
or it can be defined as the locations where wave-front propagating from the outline shape make sharp corners. \cite{blum1967transformation}
This last conceptualization is especially relevant because the naive toolpath generation method consists precisely in equidistant wave-fronts from the outline.
The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
See \cref{MAT_explanation}.

@@

We then also discretize parabolic edges and edges generated by two concave outline vertices into edges approximately as long as some constant $d^\text{discretization}$.
See \cref{discretization} and the middle of \cref{shape_decomposition_st}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the ST capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
%; see \cref{mat_3d}.

@@

\subsection{Center classification}\label{sec_center_classification}
The naive method of performing constant width offset produces large overfill and underfill areas on central regions of the ST.
These central regions present themselves as upper ridges in the mountains of the UoC surface.
This sections covers what parts of the UoC will be marked as being central, as opposed to peripheral.

@@

For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using a naive strategy of constant bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the naive toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.
Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.

\begin{figure}
\centering
\includegraphics[width=.5\columnwidth]{sources/method/naive_overfill_underfill.pdf}
\caption{
Overfill and underfill areas in a naive beading using a constant bead width $w$ of a wedge area with vertex angle $\beta$.
The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).
The bisector angle $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
}
\label{naive_overfill_underfill}
\end{figure}

>>>>

\section{Method}
\subsection{Overview}
The simple technique consists of consecutive inward offsets from the outline using a uniform bead width.
These offsets can be generated from the medial axis transform (MAT).
The medial axis transform can be conceptualized as the skeleton of the mesh of the volume defined by the union of all cones (with the same incline) which are touching the input shape. \cite{blum1967transformation}
The constant width insets are the intersections between the Union of Cones (UoC) and horizontal planes at regular intervals.
We can therefore use the MAT to efficiently calculate the consecutive offsets which define the uniform toolpathing. \cite{eiamsa2003toward}

For the uniform offsetting technique the overfill and underfill problems arise in the center,
because constant widths inward steps might not resolve to the arbitrary diameter of the outline shape.
Our framework can be seen as a way to change the mesh of the UoC such that the heights at the center are aligned with the slicing planes.

@@

Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous,
or it can be defined as the locations where wave-front propagating from the outline shape make sharp corners. \cite{blum1967transformation}
This last conceptualization is especially relevant because the uniform toolpath generation method consists precisely in equidistant wave-fronts from the outline.
The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
See \cref{MAT_explanation}.

@@

We then also discretize parabolic edges and edges generated by two concave outline vertices into edges approximately as long as some constant $d^\text{discretization}$.
See the middle of \cref{shape_decomposition_st}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of an edge in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the ST capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
%; see \cref{mat_3d}.

@@

\subsection{Center classification}\label{sec_center_classification}
The simple technique of performing uniform width offset produces large overfill and underfill areas on central regions of the ST.
These central regions present themselves as upper ridges in the mountains of the UoC surface.
This sections covers what parts of the UoC will be marked as being central, as opposed to peripheral.

@@

For a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$, which corresponds to overfill areas and underfill areas the size of $\nicefrac12 w^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w$.
See \cref{naive_overfill_underfill}.
The bisector angle is therefore an exact measure of the amount of overfill and underfill in the uniform toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.
Our framework will decide on a beading at all of the marked nodes in `the center' nodes and apply the beading outward to the unmarked nodes.

\begin{figure}
\centering
\includegraphics[width=.5\columnwidth]{sources/method/naive_overfill_underfill.pdf}
\caption{
Overfill and underfill areas in a simple toolpathing using a uniform bead width $w$ for a wedge area with vertex angle $\beta$.
The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).
The bisector angle $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
}
\label{naive_overfill_underfill}
\end{figure}

### 2019-08-26 5_generalization.tex
naive method ==> uniform technique

\paragraph{Naive Beading Strategy}
We can define a beading strategy which emulates the naive method by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

@@

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the naive tool paths.
We therefore base the beading strategy on the bead count $q^-(d)$ defined by the naive beading strategy.
\citeauthor{Jin2017JMS} replace two beads from the naive toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

@@

\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the naive strategy will still hold approximately.

>>>>

\paragraph{Uniform Beading Strategy}
We can define a beading strategy which emulates the uniform width offsetting technique by disabling the marking of edges, so that we never employ transitioning.
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w_\text{pref}} + \frac12 \right\rfloor \\
W(n,d)_i &= w_\text{pref} \text{ for all } i 
%\\
%L(n,d)_i &= w_\text{pref} \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}

@@

\paragraph{Centered}
We can emulate the method by \citeauthor{Jin2017JMS}, by transcribing how they deviate from the uniform width toolpaths.
We therefore base the beading strategy on the bead count $q^-(d)$ defined by the uniform beading strategy.
\citeauthor{Jin2017JMS} replace two beads from the uniform toolpaths by a single one when the radius between the center and either of those beads falls short of $r_\text{min} = 0.8 w_\text{pref}$.
Conversely, they place an extra bead when the radius between the center and either of the innermost beads exceeds $r_\text{max} = 1.25 w_\text{pref}$.\cite{Jin2017JMS}
We emulate the rounded polygonal path rerouting they define by supplying a transition length which results in a discretized version of the rounded polygon segment.

@@

\paragraph{Inward distributed}
For example, we can choose 
$$M(n,d)_i = \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )$$
to distribute the discrepancy over the innermost $2N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed strategy to a central region and have the nominal bead width $w_\text{pref}$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform strategy will still hold approximately.

### 2019-08-26 6_validation.tex
naive method ==> uniform technique

\section{Validation}
In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
The data set is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
We generated the toolpaths on these 300 outline shapes using the naive technique as implemented by Clipper and compare it to the 4 strategies discussed in \cref{sec_generalization}, namely 'Constant bead count' strategy with a bead count of $C=4$, the 'Centered' beading strategy, the 'Evenly distributed', and the 'Inward distributed' beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.

\subsection{Computational analysis}
Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
The naive method was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
The computation time of each slice from the data set was recorded for the "Inward distributed" and "Naive" strategy. 
\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.

@@

From the experimental results shown in \cref{computime} we can see that both our framework and the naive method as implemented using Clipper have an expected running time of approximately $2*10^{-5} n \log n$ seconds.
The computation time is approximately five times the computation time of the naive method, which puts it in the same order of magnitude.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
\caption{Naive}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
\caption{Center}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the widths for various beading strategies.
Extrusion beads in gray tones,
overfill in orange,
underfill in azure,
narrow beads in blue
and wide beads in red.
}
\label{visualized_accuracy}
\end{figure*}

We calculated the total overfill and underfill areas of the different toolpath strategies applied on the data set. 
The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
The "Inward distributed" strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
This is lower compared to the "Naive" strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.

@@

\caption{
Results of computational analysis of the results from applying the naive method and various beading strategies using our framework to the data set.
Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
}
\end{figure*}

@@

\begin{figure}
\centering
\begin{subfigure}{\columnwidth}\centering
\setlength{\figwidth}{\columnwidth}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
\caption{Wedge}\label{print_wedge}
\end{subfigure}
\caption{
A wedge shape printed using the naive strategy, center deviation strategy and the inward distributed strategy.
The naive and center deviation strategy show problems around certain model diameters.
}
\label{wedge_print}
\end{figure}

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
}
\caption{Naive}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
}
\caption{Center deviation}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the naive strategy, center deviation strategy and the inward distributed strategy.
The naive method produces distinct underfill areas.
The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed strategy produces the least defects.
}
\label{prints}
\end{figure}

>>>>

\section{Validation}
In order to test our framework, we have assembled a data set of different types of 3D models, ranging over various applications and various types of geometry.
The data set is described in detail in the accompanying data in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices from the total set of slices for analysis.
We generated the toolpaths on these 300 outline shapes using the uniform technique as implemented by Clipper and compare it to the 4 strategies discussed in \cref{sec_generalization}, namely 'Constant bead count' strategy with a bead count of $C=4$, the 'Centered' beading strategy, the 'Evenly distributed', and the 'Inward distributed' beading strategy, using a nominal bead widths of $w_\text{pref}] = \SI{0.4}{\milli\meter}$.

\subsection{Computational analysis}
Experiments were performed on an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} using a single core and \SI{16.3}{\giga\byte} memory.
The uniform width offsetting technique was implemented using the state-of-the-art polygon offset library Clipper. \cite{johnson2014clipper}
The computation time of each slice from the data set was recorded for the uniform technique and the inward distributed strategy. 
\cref{computime} shows these computation times of each layer plotted against the vertex count of the layer.

@@

From the experimental results shown in \cref{computime} we can see that both our framework and the uniform technique as implemented using Clipper have an expected running time of approximately $2*10^{-5} n \log n$ seconds.
The computation time is approximately five times the computation time of the uniform technique, which puts it in the same order of magnitude.

@@

\begin{figure*}
\centering
\setlength{\figwidth}{0.19\textwidth}
\setlength{\figheight}{0.283\textwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_naive_widths.png}
\caption{Uniform}\label{TEST_naive_accuracy}
\end{subfigure}
%\begin{subfigure}{\figwidth}\centering
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_accuracy.png}
%\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_SingleBead_widths.png}
%\caption{Single}\label{TEST_SingleBead_accuracy}
%\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Constant_widths.png}
\caption{Constant}\label{TEST_Constant_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Center_widths.png}
\caption{Center}\label{TEST_Center_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_accuracy.png}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/TEST_Distributed_widths.png}
\caption{Distributed}\label{TEST_Distributed_accuracy}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_accuracy.png}
\includegraphics[width=\columnwidth]{sources/validation/gMAT_example/TEST_InwardDistributed_widths.png}
\caption{Inward}\label{TEST_InwardDistributed_accuracy}
\end{subfigure}
\begin{subfigure}{.04\columnwidth}\centering
\vspace{4.7cm}
\includegraphics[height=\figheight]{sources/validation/gMAT_example/widths_legend.png}
\end{subfigure}
\caption{
Visualizing the overfills and underfills and the widths for various beading strategies.
Extrusion beads in gray tones,
overfill in orange,
underfill in azure,
narrow beads in blue
and wide beads in red.
}
\label{visualized_accuracy}
\end{figure*}

We calculated the total overfill and underfill areas of the different toolpath strategies applied on the data set. 
The overfill and underfill areas as a percentage of the total area of the slices from the data set are illustrated in \cref{over_underfill}.  
The inward distributed strategy has a calculated overfill of 0.24\% and an underfill of 0.17\%.
This is lower compared to the uniform strategy, which results in 1.2\% overfill and 1.7\% underfill when applied to the data set.

@@

\caption{
Results of computational analysis of the results from applying the uniform width technique and various beading strategies using our framework to the data set.
Note the use of a logarithmic scale on the Y-axes and on some of the X-axes as well.
}
\end{figure*}

@@

\begin{figure}
\centering
\begin{subfigure}{\columnwidth}\centering
\setlength{\figwidth}{\columnwidth}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_naive_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_center_edited.png}
\includegraphics[width=\figwidth]{sources/applications/P3_print_wedge_inward_edited.png}
\caption{Wedge}\label{print_wedge}
\end{subfigure}
\caption{
A wedge shape printed using the uniform strategy, center deviation strategy and the inward distributed strategy.
The uniform and center deviation strategy show problems around certain model diameters.
}
\label{wedge_print}
\end{figure}

\begin{figure}
\centering
\setlength{\figheight}{.38\columnwidth}
\setlength{\figheightTwo}{.47\columnwidth}
\setlength{\figwidth}{0.32\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_naive.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_naive_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_naive_edited.png}
}
\caption{Uniform}\label{print_naive}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_center.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_center_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_center_edited.png}
}
\caption{Center deviation}\label{print_center}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[height=\figheightTwo]{sources/applications/gMAT_inward.png}
\includegraphics[height=\figheight]{sources/applications/P3_print_hex_inward_edited.png}
\censorbox{
\includegraphics[width=\figwidth]{sources/applications/P3_print_UM_inward_edited.png}
}
\caption{Inward distributed}\label{print_inward}
\end{subfigure}
\caption{
Test shapes printed using the uniform strategy, center deviation strategy and the inward distributed strategy.
The uniform technique produces distinct underfill areas.
The center deviation strategy shows some defects due to inaccurate control of extremal deposition widths.
The inward distributed strategy produces the least defects.
}
\label{prints}
\end{figure}
